%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%	Copyright (c) 2021 Jitin Nair
%-----------------------------------------------------------------------------------------------------------------------------------------------%

\documentclass[a4paper,11pt]{article}

%----------------------------------------------------------------------------------------
%	PACKAGES & SELECTION
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[margin=1.5cm]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}
\usepackage{fontawesome5}
\usepackage[unicode, draft=false]{hyperref}

% Setup hyperref
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

% Custom section formatting
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{8pt}{8pt}

% List settings
\setlist[itemize]{leftmargin=1.5em, nosep, itemsep=2pt, label=--}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	HEADER
%----------------------------------------------------------------------------------------
\begin{center}
    {\Huge \scshape Shaun Paul} \\[5pt]
    \href{mailto:shaunpaul382@.com}{\faEnvelope \ shaunpaul382@.com} \ $|$ \ 
    \href{tel:+4915218960695}{\faMobile \ +49 1521 8960695} \\
    \href{https://www.linkedin.com/in/shaun-paul-a15a32251}{\faLinkedin \ LinkedIn} \ $|$ \ 
    \href{https://scholar.google.com/citations?user=43CupecAAAAJ&hl=en}{\faGraduationCap \ Google Scholar} \ $|$ \ 
    \href{https://orcid.org/0009-0002-6161-8018}{\faOrcid \ ORCID}
\end{center}

%----------------------------------------------------------------------------------------
%	RESEARCH INTERESTS
%----------------------------------------------------------------------------------------
\section{Research Interests}
AI safety and alignment, human-AI interaction, behavioral interventions for trust calibration, experimental evaluation of AI systems, and AI governance. Focused on developing proactive safety mechanisms for human-AI collaboration.

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\textbf{Universität des Saarlandes}, Germany \hfill \textit{Oct 2024 -- Present} \\
Master of Science in Cybersecurity \\
\textit{Relevant Coursework:} Formal Methods for AI Alignment, Generative AI for Interactive Systems, Cryptography, Network Security, Secure Systems Design.

\textbf{NMAM Institute of Technology}, India \hfill \textit{2020 -- 2024} \\
Bachelor of Engineering in Information Science \& Engineering \\
GPA: 8.93/10.0 (Equivalent to 1.5 in German grading system) \\
\textit{Honors:} \textbf{Project of the Year} (Awarded by NMAMIT Alumni Association).

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
\section{Publications}
[1] M.G. Rao, S.K. Rashmitha, R.H. Sanjana, S. Prabhu, S. Noronha, and \textbf{S. Paul}, "Innovative Solutions: LBPH Technology Driving the Future of Intelligent Security Systems," in \textit{Proc. IEEE Int. Conf. Women Innovation, Technology \& Engineering (IEEE ICWITE)}, 2024.

[2] M.G. Rao, S. Noronha, R. Shetty, \textbf{S. Paul}, S. Shetty, and R.V. Shetty, "CNN-Based Classification for Autonomous Identification of RL Disease," \textit{AIP Conf. Proc.}, vol. 3278, no. 1, p. 020027, 2024.

%----------------------------------------------------------------------------------------
%	RESEARCH EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Research Experience}
\textbf{Research Fellow | AI Safety Saarland} \hfill \textit{Nov 2025 -- Present} \\
\textit{Supervisor: Dr. Siddharth Mehrotra (University of Amsterdam)}
\begin{itemize}
    \item Investigating trust calibration in human-AI interaction through \textbf{TrustGuard}, an insurance-inspired interface mechanism for reducing over-reliance.
    \item Designing between-subjects randomized controlled experiments (target n=200+) using Qualtrics for data collection and custom web-based decision tasks.
    \item Developing behavioral interventions combining interface friction (digital premiums/deductibles) with real-time AI confidence displays.
    \item Implementing experimental platform using \textbf{Python (FastAPI backend), JavaScript (React frontend)}, analyzing results with \textbf{pandas, scipy.stats, and matplotlib}.
    \item Integrating behavioral economics, legal theory, and HCI design principles to inform proactive AI safety mechanisms.
    \item Preparing manuscript for \textbf{CHI 2027} submission on appropriate trust in AI systems.
\end{itemize}

%----------------------------------------------------------------------------------------
%	TEACHING & OUTREACH
%----------------------------------------------------------------------------------------
\section{Teaching \& Outreach}
\textbf{Facilitator | AI Safety Saarland} \hfill \textit{May 2026 -- Jul 2026 (Selected)}
\begin{itemize}
    \item Selected to guide 15+ students through the introductory AI Safety Fellowship covering alignment challenges, scaling problems, and oversight mechanisms.
    \item Will deliver technical explanations on compute governance, semiconductor supply chain vulnerabilities, and geopolitical dynamics in frontier AI development.
    \item Will facilitate structured discussions translating complex AI safety research into accessible materials for interdisciplinary audiences.
\end{itemize}

\newpage

\textbf{Teaching Assistant (Visiting Instructor) | CET Prep Program} \hfill \textit{Jun 2024 -- Aug 2024}
\begin{itemize}
    \item Designed and delivered technical sessions on computer networks and programming for 50+ students from underserved communities.
    \item Developed exam-focused curriculum breaking down advanced computing concepts, achieving a 32\% admission rate into government-funded graduate programs.
    \item Recognized with a teaching excellence certificate for measurable improvements in student outcomes.
\end{itemize}

%----------------------------------------------------------------------------------------
%	ACADEMIC PROJECTS
%----------------------------------------------------------------------------------------
\section{Academic Projects}
\textbf{Cloud Storage: Confidentiality Locking \& Optimized Deduplication} \hfill \textit{2024}
\begin{itemize}
    \item Designed and implemented a secure cloud storage architecture integrating data deduplication with encryption.
    \item Achieved ~30\% reduction in storage utilization while preserving data confidentiality and integrity.
    \item Implemented access control and confidentiality locking using cryptographic primitives.
    \item Awarded \textbf{Project of the Year} by the NMAMIT Alumni Association.
\end{itemize}

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS
%----------------------------------------------------------------------------------------
\section{Technical Skills}
\textbf{Programming:} Python, C, Java, Bash. \\
\textbf{AI \& LLM Tools:} Ollama (Local LLM deployment), OpenHands (AI Agents), LangChain (Orchestration), Hugging Face, Prompt Engineering, Model Quantization. \\
\textbf{Research Tools:} Qualtrics (experimental design), Git (version control), Docker, statistical analysis (scipy.stats). \\
\textbf{Security \& Systems:} Cryptography, Network Security, Access Control, Threat Modeling, Cloud Security. \\
\textbf{Specializations:} Human-AI interaction experiments, behavioral economics frameworks, experimental design, data analysis, quantitative methods.

%----------------------------------------------------------------------------------------
%	LANGUAGES & ADDITIONAL EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Languages}
\textbf{English} (C1 – Professional Proficiency) \quad $|$ \quad \textbf{German} (A2 – Conversational)

\section{Additional Experience}
\textbf{Network \& IT Support Intern} | Udupi Fastnet Pvt. Ltd. \hfill \textit{Jul 2023 -- Aug 2023} \\
Enterprise network management, CDN operations, and DNS configuration.

\textbf{Cybersecurity Intern} | Exposys Data Labs (Remote) \hfill \textit{Jun 2023 -- Jul 2023} \\
Applied Triple DES encryption for secure image transmission systems.

\vfill
\center{\footnotesize Last updated: \today}

\end{document}
